Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-09-23 eg6-letters/long-paper/AdHoc/AnswerAdHoc.tex
Further answers to comments for long paper

   \textcolor{blue}{This is given in eq. 3.6 and tab. 3.1 of the analysis note, we decided not to go to this level 
   of details.}

@@

   \textcolor{blue}{the intent of this figure is comparing the simulation to the real data. What you propose is 
different and would show the shape of the background. We do not have a way to show this background from experimental 
data. We provided some of this information by email, but are not convinced it is a useful addition. The document is
already going into a lot of technical details already.}

@@

\item  In Section 4.1, your choice to use the present tense here is quite jarring, especially since you don't make a
distinction between the original CLAS, the upgraded CLAS-12 detector. Please consider switching to past
tense here and making that distinction explicit. Furthermore, it would be good to state that these data came
from the EG6 run period, and give the year that they were collected.
   \textcolor{blue}{...}

5. Line 147: "Its historic use to measure DVCS in many different configurations made it an ideal place for this
new DVCS measurement."
This is not an informative claim. CLAS can be ideal for DVCS for many reasons, but you're pretty much
giving a tautology here.
   \textcolor{blue}{The information is that CLAS has been used for other DVCS measurements in the past. It seems
rather relevant when showing results for a new DVCS channel.}

\item  Section 5.1: "In particular, it serves for the identification of the protons."
Are you referring to the time-of-flight detection of the electron or the proton? Perhaps separate sections for
electron ID and proton ID are warranted. Furthermore, you have no section on the ID of 4 He in the RTPC.
We know that this is covered in the RTPC NIM, but a paragraph would be nice.
   \textcolor{blue}{...}

\item  Line 238: "In principle, a selection based on two or three variables can be used to guaranty the exclusivity of
the process."
In exclusive DVCS, you measure the momentum vectors of 3 particles of known ID, i.e. 9 quantities. Exclu-
sivity requires both energy and momentum conservation, i.e. 4 constraints. Where do "2 or 3" come from?
That is a vague statement.
   \textcolor{blue}{This is incorrect, 1 constraint is enough, you can ensure exclusivity by only cutting on missing 
energy, if it is 0 the process is exclusive. Due to the effects of resolution this is usually never a good solution
and 2-3 variables are used, often mass and missing momentum for instance. However, we agree the statement was a bit 
vague and we changed this sentence.}

\item  Line 302: "As it is not obvious which solution is best. . ."
What is obvious is that this is not an issue of correct or incorrect, but one of possible bias introduced to your
BSA from your poor t resolution. Please rephrase the paragraph in these terms, and state what systematic
uncertainty is introduced from the limitations in your ability to reconstruct t. If this effect introduces negligible
uncertainty on the BSA, that's fine, but make that argument clear.
   \textcolor{blue}{...}

\item  Table 1 is mildly misleading, simply because the beam polarization is a relative uncertainty, while the others
are absolute uncertainties (if we understand correctly). Perhaps it is better to pull beam polarization out of
the middle of the table and put it somewhere else so it can be understood as distinct.
That 3.5\% is a multiplicative factor, right?
   \textcolor{blue}{...}

>>>>

   \textcolor{blue}{This is given in eq. 3.6 and tab. 3.1 of the analysis note, there is no $\phi$-dependence 
   in the generation. We decided not to go to this level 
   of details in this paper as the parameters have no relevant physics signification.}

@@

   \textcolor{blue}{The intent of this figure is to compare the simulation to the real data, to assess the 
quality of the simulation. What you propose would not be more useful, it would serve a different purpose:
showing the shape of the background. We do not have a way to show this background from experimental 
data so it would not allow to assess the same information. We provided some of the numbers by email, 
but are not convinced it highlights anything important about the analysis. The document is
already going into a lot of technical details, probably more than most comparable long paper and prefer not 
to go to that extend.}

@@

\item  In Section 4.1, your choice to use the present tense here is quite jarring, especially since you don't make a
distinction between the original CLAS, the upgraded CLAS-12 detector. Please consider switching to past
tense here and making that distinction explicit. Furthermore, it would be good to state that these data came
from the EG6 run period, and give the year that they were collected.
   \textcolor{blue}{This section has been modified.}

5. Line 147: "Its historic use to measure DVCS in many different configurations made it an ideal place for this
new DVCS measurement."
This is not an informative claim. CLAS can be ideal for DVCS for many reasons, but you're pretty much
giving a tautology here.
   \textcolor{blue}{The information is that CLAS has been used for other DVCS measurements in the past. It seems
to be a relevant information when showing results for DVCS on a new target.}

\item  Section 5.1: "In particular, it serves for the identification of the protons."
Are you referring to the time-of-flight detection of the electron or the proton? Perhaps separate sections for
electron ID and proton ID are warranted. Furthermore, you have no section on the ID of 4 He in the RTPC.
We know that this is covered in the RTPC NIM, but a paragraph would be nice.
   \textcolor{blue}{We made the change and clarified the detection of protons and helium nuclei.}

\item  Line 238: "In principle, a selection based on two or three variables can be used to guaranty the exclusivity of
the process."
In exclusive DVCS, you measure the momentum vectors of 3 particles of known ID, i.e. 9 quantities. Exclu-
sivity requires both energy and momentum conservation, i.e. 4 constraints. Where do "2 or 3" come from?
That is a vague statement.
   \textcolor{blue}{This is incorrect, 1 constraint is enough, you can ensure exclusivity by only cutting on missing 
energy, if it is 0 the process is exclusive. Due to the effects of resolution this is usually never a good solution
and 2-3 variables are used, often missing mass and missing momentum for instance. However, we agree the statement was 
vague and not very useful, we changed this sentence completely.}

\item  Line 302: "As it is not obvious which solution is best. . ."
What is obvious is that this is not an issue of correct or incorrect, but one of possible bias introduced to your
BSA from your poor t resolution. Please rephrase the paragraph in these terms, and state what systematic
uncertainty is introduced from the limitations in your ability to reconstruct t. If this effect introduces negligible
uncertainty on the BSA, that's fine, but make that argument clear.
   \textcolor{blue}{We added a sentence about the fact that no error is associated to 
this study.}

\item  Table 1 is mildly misleading, simply because the beam polarization is a relative uncertainty, while the others
are absolute uncertainties (if we understand correctly). Perhaps it is better to pull beam polarization out of
the middle of the table and put it somewhere else so it can be understood as distinct.
That 3.5\% is a multiplicative factor, right?
   \textcolor{blue}{We changed the order of the lines and the presentation in the table to make it clearer.}

### 2020-09-23 eg6-letters/long-paper/prc-dvcshelium.tex
Further answers to comments for long paper

The CLAS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
perform this measurement however, several instrumentation challenges needed to be resolved. First, to
measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
radial time projection chamber (RTPC) was installed to measure the
helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
will review the important elements of this detection setup.

@@

CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
accelerator facility (CEBAF). CLAS is specifically designed to study the multi-particles final states
that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement. CLAS is composed of six identical radial 
sectors separated by coils of toroidal magnets, with each sector made of four detectors 
as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
are placed between the torus magnet to reconstruct the charged particles' tracks and 
calculate their momentum. An array of scintillators is placed behind the drift chambers to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
In forward region, from 8 to 45 degree, these two detectors are complemented with 
Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
important for electron identification.

@@

Altogether, CLAS provides a large acceptance of about $2\pi$ steradians for momenta 
starting at 200 MeV/c. During the nuclear DVCS experiment,
the beam energy was highest for CLAS with 6.064 GeV, while the beam intensity varied
between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
During the experiment, the data acquisition operated at a rate of about 3 kHz with about 70\% live-time
using an inclusive electron trigger.

@@

The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
of the electron and the signal measured in both the Cerenkov counter and electromagnetic calorimeter
provide the identification. A signal of good quality is also required in the 
time-of-flight system, which serves as a time reference for other detectors. In particular, it 
serves for the identification of the protons. Several 
fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
or the solenoid, as well as to reject the edges of the detectors, where efficiency is rapidly 
decreasing. Kinematic corrections are also applied to the electrons and protons to correct for energy loss
and biases in calibration, they are at subpercent level except for protons below 500 MeV/c for which they
go up to 10\% at the detection limit of 200 MeV/c.

@@

@@

\begin{table}[tbp]
\begin{center}
	\begin{tabular}{|m{4cm}|m{2cm}<{\centering}|m{2.3cm}<{\centering}|m{3.7cm}<{\centering}|}
\hline
\bf Systematic source & \bf  Coherent channel  & \bf Incoherent channel & \bf Type of systematic 
error\\
\hline
DVCS cuts & 8 $\%$ &  6 $\%$ & bin to bin\\
\hline
Data binning & 5.1$\%$ & 7.1$\%$ &bin to bin\\
\hline
Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
\hline
$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ &bin to bin\\
\hline
%Beam charge asymmetry &  ~~~~~1.1$\%$&  ~~~~~1.1$\%$\\
%\hline
Radiative corrections &  0.1$\%$ & 0.1$\%$ & bin to bin\\
\hline
\textbf{Total} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ &bin to 
bin\\
\hline
\end{tabular}
\caption{The systematic uncertainties on the measured coherent and incoherent 
beam-spin asymmetries at $\phi = 90^{\circ}$.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}

As discussed above, the best way to define $t$ in the incoherent channel is not completely
straightforward. As can be seen in Fig. \ref{fig:InCohDiag}, 
we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
identical, but experimentally we face some issues. The measurement of $t$ is less precise than
$t^\prime$ because it involves the photon rather than charged particles. However, the 
exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
we studied the difference between the two results by analyzing the data independently using the two 
definitions. We found no significant difference between them, as it is 
illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$,
which is the correct definition with the slightly poorer resolution.

>>>>

The CLAS nuclear DVCS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
perform this measurement however, several instrumentation challenges needed to be resolved. First, to
measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
radial time projection chamber (RTPC) was installed to measure the
helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
will review the important elements of this detection setup.

@@

CLAS \cite{Mecking:2003zu} was installed in the hall-B of the JLab continuous electron beam 
accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles final states
that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement. CLAS was composed of six identical radial 
sectors separated by coils of toroidal magnets, with each sector made of four detectors 
as shown in Fig. \ref{fig:CLAS}. Three regions of drift chambers \cite{Mestayer:2000we} 
were placed between the torus magnet to reconstruct the charged particles' tracks and 
calculate their momentum. An array of scintillators was placed behind the drift chambers to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors covered the polar angle from 8 to 142 degrees. 
In the forward region, from 8 to 45 degree, these two detectors were complemented with 
Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
important for electron identification and photon detection.

@@

Altogether, CLAS provided a large acceptance for momenta 
starting at 200 MeV/c. The nuclear DVCS experiment took place from October to December 2009,
the beam energy was 6.064 GeV, while the beam intensity varied
between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
During the experiment, the data acquisition operated at a rate of about 3 kHz with about 70\% live-time
using an inclusive electron trigger.

@@

The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
of the electron and the signal measured in both the Cerenkov counter and electromagnetic calorimeter
provide the identification. A signal of good quality is also required in the 
time-of-flight system, which serves as a time reference for all detectors. 
Protons are detected with the baseline CLAS detectors as well, the drift chamber measures the kinematic 
of the proton and the time-of-flight system ensure its identification.
Several 
fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
or the solenoid, as well as to reject the edges of the detectors, where efficiency is rapidly 
decreasing. Kinematic corrections are also applied to the electrons and protons to correct for energy loss
and biases in calibration, they are at subpercent level except for protons below 500 MeV/c for which they
go up to 10\% at the detection limit of 200 MeV/c.

@@

The helium-4 nuclei are detected with the RTPC using a series of constraints on the quality
of the track reconstruction. As the chamber was operated at low gain and had very low efficiency 
for protons, we did not apply further identification cuts for the helium-4 nuclei 
detection~\cite{Dupre:2017upj}.

@@

\begin{table}[tbp]
\begin{center}
	\begin{tabular}{|m{4cm}|m{2cm}<{\centering}|m{2.3cm}<{\centering}|m{3.7cm}<{\centering}|}
\hline
\bf Systematic source & \bf  Coherent channel  & \bf Incoherent channel & \bf Type of systematic 
error\\
\hline
Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
\hline
\hline
DVCS cuts & 8 $\%$ &  6 $\%$ & Bin to bin\\
\hline
Data binning & 5.1$\%$ & 7.1$\%$ & Bin to bin\\
\hline
$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ & Bin to bin\\
\hline
Radiative corrections &  0.1$\%$ & 0.1$\%$ & Bin to bin\\
\hline
\hline
\textbf{Total bin to bin} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ & Bin to 
bin\\
\hline
\end{tabular}
\caption{The systematic uncertainties on the measured coherent and incoherent 
beam-spin asymmetries at $\phi = 90^{\circ}$.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}

An extra problem that was studied is the best way to define $t$ in the incoherent channel, 
which is not completely straightforward. As can be seen in Fig. \ref{fig:InCohDiag}, 
we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
identical, but experimentally we face some issues. The measurement of $t$ is less precise than
$t^\prime$ because it involves the photon rather than charged particles. However, the 
exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
we studied the difference between the two results by analyzing the data independently using the two 
definitions. We found no significant difference between them, as it is 
illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$ as it is based on the 
rigorous definition. Since the effect of resolution appears small and is partly accounted for
in the systematic error associated to the DVCS cuts, we decided not to associate an extra
systematic error based on this study.
